Manuscript_Github_Pchabaudi_compBerghei

### 2022-08-08 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_compBerghei.Rmd
Perform prop.tests on chab samples

>>>>

Hypothesis: There is a difference in the transcription level of L-form pirs as a proportion of all S/L-form pirs between Asexual Schizont samples and non-schizont samples

```{r}
chab_tpm_subfam.L.df.long <- chab_tpm_subfam.df.long %>% 
  filter(!subfam == 'ancestral (n = 1)') %>% 
  mutate(subfam_L = grepl(subfam, pattern = '^L')) %>% 
  group_by(transmission, time, name, sample, subfam_L) %>% 
  summarise(sum_tpm = sum(tpm)) %>% 
  group_by(sample) %>% 
  mutate(sum_tpm_all = sum(sum_tpm)) %>% 
  filter(subfam_L)

chab_tpm_subfam.L.df.long %>% 
  group_by(sample) %>% 
  mutate(prop_L = sum_tpm/sum_tpm_all) %>% 
  arrange(desc(prop_L))

bind_rows(
  lapply(str_subset(unique(chab_tpm_subfam.L.df.long$sample), 
                    pattern = 'rMT(?!_sch.culture)'),
         function(sample.name){
           bind_rows(
             lapply(c('rMT_sch.culture_1', 
                      'rMT_sch.culture_2', 
                      'rMT_sch.culture_3'), 
                    function(sch.cult){
                      L_forms <- c(chab_tpm_subfam.L.df.long$sum_tpm[
                        chab_tpm_subfam.L.df.long$sample == sample.name
                      ],
                      chab_tpm_subfam.L.df.long$sum_tpm[
                        chab_tpm_subfam.L.df.long$sample == sch.cult
                      ])
                      SorL_forms <- c(chab_tpm_subfam.L.df.long$sum_tpm_all[
                        chab_tpm_subfam.L.df.long$sample == sample.name
                      ],
                      chab_tpm_subfam.L.df.long$sum_tpm_all[
                        chab_tpm_subfam.L.df.long$sample == sch.cult
                      ])
                      test.stat <- prop.test(L_forms, SorL_forms,
                                             alternative = 'less')
                      data.frame(comp = paste0(sample.name, '-', sch.cult),
                                 pval = test.stat$p.value)
                    })
           )
         })
)%>% 
  mutate(padj = round(p.adjust(pval), digits = 5),
         pval = round(pval, digits = 5)) %>% 
  arrange(desc(padj))
```

```{r berg_prop_test}
